Using traffic analysis to identify The Second Generation Onion Router

### 2011-01-23 thesis/experiment.tex
Some bug fixes and syntax errors, add in appendices, add units to lstlistings values, escape '_'s, better use of \verb, \botomrule typo fixed, more section rearrangement

Weka is data mining software which includes tools for classification of data
sources using a wide variety of machine learning algorithms
\parencite{Hall:2009p7662}.

@@

VirtualBox is virtualization software that allows the running of a guest
operating system in its own environment on another host operating system
\parencite{:fk}.  It supports snapshots and a remote control facility which
make it useful for running repetitions in an experimental environment
\parencite{:uq}.

@@

Ruby is an object orientated, dynamic programming language which is useful for
quick prototyping and as such has been used to automate the simulation
described in this experiment \parencite{:2010uq}.

@@

Selenium is a web testing framework with a number of components that allow
developers to write automated tests of web applications using most modern web
browsers \parencite{:2010ys}. Using the Selenium framework one can mimic the
actions of an actual user interacting with a web site.

@@

\begin{tabular}{lrr}
  \toprule
  Role & Operating System Version & IP Address\\
  \midrule
  Client Host & Desktop & 192.168.0.100\\
  Server Host & Desktop & 192.168.0.001\\
  Tor Host & Desktop & 192.168.0.102\\
  \midrule
  Sniffing System & Server & 192.168.0.200\\
  \midrule
  Client Guest & Desktop & 192.168.0.16\\
  Server Guest & Server & 192.168.0.17\\
  Tor Network Guest & Server & 192.168.0.18\\
  \botomrule
  \label{table:hosts}
\end{tabular}

@@

@@

The sniffing system was based on a basic installation of the Ubuntu 10.04 server
operating system with no additional packages installed.

An init.d script was installed to execute the tcpdump program with a specific
filter string after the system had powered on. All capture files were limited to
1mb in size and put into a time stamped directory. To ensure that only relevant
packets were collected the filter string was tuned for each phase of the
experiment. The filter string for each phase is shown below.

Phase 1:
\begin{lstlisting}[language=sh]
dst port 443
\end{lstlisting}

Phase 2 and 3:
\begin{lstlisting}[language=sh]
dst port 5000-5015
\end{lstlisting}

@@

All the host systems are configured identically. The following procedure is
carried out to prepare a host system.

\begin{itemize*}
  \item Install Ubuntu 10.04 Desktop Operating System
    \begin{itemize*}
      \item Use entire disk
      \item Set time zone to GMT +8 WST (Perth)
    \end{itemize*}
  \item Turn off automatic package updates
  \item Turn off power saving features
  \item Install OpenSSH Server
  \item Add Virtual Box repository to sources.lst
  \item Update sources and install Virtual Box
  \item Ensure Virtual Box starts with system and disable all other start
    up applications
\end{itemize*}

One of the host systems is set aside as a management system, which is
responsible for ensuring the experiment runs and restarts it if there are any
problems. On this machine a private ssh key is created, and copied to the
authorized keys file on all other hosts. This allows the management system to
connect to all the other systems and issue commands without user interaction.

The management script runs on the management system to watch the experiment's
progress. This is a simple Ruby script which uses SSH to control the other Host
systems and opens a socket which waits for a connection that indicates that the
experiment has finished. Every time it starts the experiment, it rolls back
each virtual machine to a preconfigured snapshot. If the experiment takes too
long, say because a virtual machine hangs or something is wrong, it will be
started without waiting for the finish condition.

@@

\subsubsubsection{Selenium}

@@

cmd=getNewBrowserSession&1=*firefoxproxy&2=http://www.google.com

@@

To get SSL certificates accepted, you must manually accept them permanently for each host. This will update the cert_override.txt and cert8.db files.

@@

\subsection{Preparation}

\subsubsection{Host Systems}

The preparation for the host operating systems is identical except for the
hostname and IP address.

Installing the Host operating system:

\begin{enumerate*}
  \item Power on machine
  \item Interrupt BIOS boot process
  \begin{enumerate*}
    \item Load default BIOS settings
    \item Set boot order to ensure CD-ROM is first
    \item Disable unnecessary boot devices
    \item Ensure system clock is correct
  \end{enumerate*}
  \item Boot from Ubuntu 10.04 Desktop cd
  \item Select the language you wish to use for installation (English) and click 'Forward'
  \item Select the region (Australia/Perth) and click 'Forward'
  \item Select an appropriate keymap (USA) and click 'Forward'
  \item Select 'Erase and use the entire disk' and click 'Forward'
  \item Enter your details, select 'Log in automatically' and click 'Forward'
\end{enumerate*}

At this point the installation will begin and should take about 35 minutes.
'Log in automatically' is selected to ensure that the experiment will continue
even if power is lost. Once installation is complete remove the CD and reboot
the system.

Configuring the Host operating system:

\begin{enumerate*}
  \item Configure the network adapter
  \item Install Virtual Box
  \item Load the guest operating system virtual machine image
\end{enumerate*}

To install Virtual Box, the following procedure is used:

\begin{enumerate*}
  \item Edit the file \verb+/etc/apt/sources.lst+ and add the line:
  \begin{verbatim}
deb http://download.virtualbox.org/virtualbox/debian lucid non-free
  \end{verbatim}
  \item Install the GPG key for the Virtual Box packages:
  \begin{verbatim}
wget -q http://download.virtualbox.org/virtualbox/debian/oracle_vbox.asc -O- | sudo apt-key add -
  \end{verbatim}
  \item Then install VirtualBox 3.2 with the command:
  \begin{verbatim}
sudo apt-get update && sudo apt-get install virtualbox-3.2
  \end{verbatim}
\end{enumerate*}

For the management system, some additional commands need to be run:

\begin{enumerate*}
  \item Generate a private ssh key for the user with the command:
    \verb+ssh-keygen+, when prompted for a password enter nothing.
  \item SSH to the other host systems on the network, and copy the contents of
    \verb+$HOME/.ssh/id_rsa.pub+ into \verb+$HOME/.ssh/authorized_keys+ on the
    destination system.
  \item Install ruby so that the management script can be run:
    \begin{lstlisting}[language=sh]
sudo apt-get install ruby rubygems
    \end{lstlisting}
  \item Ensure the script \verb+run_simulation.rb+ is started on login.
\end{enumerate*}

\subsubsection{Tor System}

Install Ubuntu 10.04 Server.

@@

The data captured was in the form of 1mb capture files which were recombined
with mergecap and processed by NetAI to produce ARFF format files for use by
Weka. Each data set were given the nominal classification 'http',
'http_over_tor' and 'https_over_tor', all other nominal attributes were removed.

>>>>

Weka is data mining software which includes tools for classification of data
sources using a wide variety of machine learning algorithms
\parencite{Hall:2009p7662}. It supports processing of an input
Attribute-Relation File Format (ARFF), a file which contains ASCII text
describing a list of items with common attributes. Items can be given an
attribute which provides a nominal classification for verification purposes.

@@

VirtualBox provides a virtualization environment that allows guest operating
systems to run in a virtual environment on a host operating system
\parencite{:fk}. It supports snapshots and a remote control facility which make
it useful for running a controlled experiment \parencite{:uq}.

@@

Ruby is an object orientated, dynamic programming language which is useful for
rapid prototyping and as such has been used to automate the simulation
described in this experiment \parencite{:2010uq}.

@@

Selenium is a web testing framework which allows automated testing of web pages
through any Javascript enabled web browser \parencite{:2010ys}. A web browser
can be controlled remotely using the Selenium Remote Control Server component,
which in turn can be controlled with a number of programming languages including
Ruby. This experiment makes use of a number of selenium scripts which
approximate user interactions with a website which trigger network traffic.

@@

\begin{tabular}{lrr}
  \toprule
  Role & Operating System Version & IP Address\\
  \midrule
  Client Host & Desktop & 192.168.0.100\\
  Server Host & Desktop & 192.168.0.001\\
  Tor Host & Desktop & 192.168.0.102\\
  \midrule
  Sniffing System & Server & 192.168.0.200\\
  \midrule
  Client Guest & Desktop & 192.168.0.16\\
  Server Guest & Server & 192.168.0.17\\
  Tor Network Guest & Server & 192.168.0.18\\
  \bottomrule
  \label{table:hosts}
\end{tabular}

@@

\subsubsection{Standard OS Installation Procedure}
\label{section:os_install}

All systems in the experiment use a variation of the Ubuntu Linux operating
system. The installation process followed is detailed below:

\begin{enumerate*}
  \item Configure system BIOS to boot from CD-ROM
  \item Insert Ubuntu operating system installation CD
  \item Select the language you wish to use for installation (English) and click
    'Forward'
  \item Select the region (Australia/Perth) and click 'Forward'
  \item Select an appropriate keymap (USA) and click 'Forward'
  \item Select 'Erase and use the entire disk' and click 'Forward'
  \item Enter the user name (John Barker), select 'Log in automatically' and click 'Forward'
\end{enumerate*}

At this point the installation will begin and should take about 35 minutes.
'Log in automatically' is selected to ensure that the experiment will continue
even if power is lost. Once installation is complete remove the CD and reboot
the system. Once booted the system is ready for further configuration.

Each system is given a statically assigned IP address, this is done by editing
the file \verb+/etc/network/interfaces+ and changing the line \verb+iface eth0 inet dhcp+
to:

\begin{lstlisting}[language=sh]
iface eth0 inet static
  address 192.168.0.16
  netmask 255.255.255.0
  network 192.168.0.0
  broadcast 192.168.0.255
\end{lstlisting}

Substituting \verb+eth0+ with the physical network interface identifier as
appropriate, and the address \verb+192.168.0.16+ with the desired value.

@@

The sniffing system is prepared as described in \ref{section:os_install} with an
Ubuntu 10.04 server CD. The base install of Ubuntu server has all the required
packages included so no additional software installation is required.

An init.d script was created to execute the tcpdump program with a specific
filter string after the system had powered on. All capture files were limited to
1mb in size and put into a time stamped directory. To ensure that only relevant
packets were collected the filter string was tuned for each phase of the
experiment. The filter string for each phase is shown below.

Phase 1:
\begin{lstlisting}[language=sh]
tcp port 443
\end{lstlisting}

Phase 2 and 3:
\begin{lstlisting}[language=sh]
tcp portrange 5000-5015
\end{lstlisting}

The capture script appears below with the filter string as required for phase 2
and 3:

\begin{lstlisting}[language=sh]
#!/bin/bash
export capture_date=`date`
cd /home/john/ssl-captures
mkdir "./${capture_date}"
tcpdump -vv -C 1 -i eth0 -w "./${capture_date}/capture.dat" tcp portrange 5001-5015
\end{lstlisting}

@@

The host systems all run an identically configured Ubuntu 10.04 desktop
operating system, except for the IP address which is configured as detailed in
\ref{table:hosts}. To support the guest operating systems, VirtualBox is
required. The procedure for installing VirtualBox is detailed below:

\begin{enumerate*}
  \item Edit the file \verb+/etc/apt/sources.lst+ and add the line:
\begin{lstlisting}[language=sh]
deb http://download.virtualbox.org/virtualbox/debian lucid non-free
\end{lstlisting}
  \item Install the GPG key for the Virtual Box packages:
\begin{lstlisting}[language=sh]
wget -q http://download.virtualbox.org/virtualbox/debian/oracle_vbox.asc -O- | sudo apt-key add -
\end{lstlisting}
  \item Then install VirtualBox 3.2 with the command:
\begin{lstlisting}[language=sh]
sudo apt-get update && sudo apt-get install virtualbox-3.2
\end{lstlisting}
\end{enumerate*}

The guest operating system images can then be created or imported from an
external disk.

\subsubsection{Server Host}

One of the host systems is set aside as a management system, which is
responsible for ensuring the experiment runs and restarts it if there are any
problems. On this machine a private SSH key is created, and copied to the
authorized keys file on all other hosts. This allows the management system to
connect to all the other systems and issue commands without user interaction.

The management script runs on the management system to watch the experiment's
progress. This is a simple Ruby script which uses SSH to control the other Host
systems and opens a socket which waits for a connection that indicates that the
experiment has finished. Every time it starts the experiment, it rolls back
each virtual machine to a preconfigured snapshot. If the experiment takes too
long, say because a virtual machine hangs or something is wrong, it will be
started without waiting for the finish condition. Figure
\ref{manager-flow-diagram} contains a diagram which outlines the basic flow of
the manager script.

\begin{figure}[H]
  \centering\includegraphics[scale=0.7]{manager-flow}
  \caption{Manager Script Flow Chart}
  \label{manager-flow-diagram}
\end{figure}

@@

\paragraph{Selenium}

@@

\begin{lstlisting}[language=sh]
cmd=getNewBrowserSession&1=*firefoxproxy&2=http://www.google.com
\end{lstlisting}

@@

To get SSL certificates accepted, you must manually accept them permanently for
each host. This will update the \verb+cert_override.txt+ and \verb+cert8.db+
files.

@@

@@

The data captured was in the form of 1mb capture files which were recombined
with mergecap and processed by NetAI to produce ARFF format files for use by
Weka. Each data set were given the nominal classification 'http',
'http\_over\_tor' and 'https\_over\_tor', all other nominal attributes were
removed.
